### 2021-09-29 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betadiversity_response@7470a928f270c48fb57fc0b7dd67471648c4edc9 🚀

This later component originates in unique species introducing their
unique interactions both between themselves, and with species that are
common to both networks. CONTINUE WITH BETA ST

@@

Here, I present a more thorough justification of the methodological
choices for the Poisot \emph{et al.} (2012) method, explain how
information about species turnover can be extracted from its
decomposition, and conduct numerical experiments to guide the
interpretation of the \(\beta\)-diversity values thus obtained. These
numerical experiments establish three core facts. First, the
decomposition responds to the correct sources of network variation;
second, the decomposition adequately captures the relative roles of
species turnover and interaction rewiring; finally, the decomposition
adequately captures the role of turnover vs.~non-turnover (like changes
in connectance) processes. Although the alternative normalization
suggested by Fründ (2021) is not without its uses, which I discuss in
conclusion, it is inadequate as a network \(\beta\)-diversity
measurement, as it introduces many confounding elements that make the
interpretation of the results more difficult, and should likely not be
used as a default.

>>>>

Yet, the precise meaning of \(\beta_{st}\), namely the importance of
species turnover in the overall dissimilarity, has been difficult to
capture, and a source of confusion for some practitioners. This is not
particularly surprising, as this component of the decomposition responds
to unique species introducing their unique interactions both between
themselves, and with species that are common to both networks. For this
reason, it is important to come up with guidelines for the
interpretation of this measure, and how to use it to extract ecological
insights.

@@

Here, I present a mathematical analysis of the Poisot \emph{et al.}
(2012) method, explain how information about species turnover and link
rewiring can be extracted from its decomposition, and conduct numerical
experiments to guide the interpretation of the \(\beta\)-diversity
values thus obtained (with a specific focus on \(\beta_{st}\)). These
numerical experiments establish three core facts. First, the
decomposition adequately captures the relative roles of species turnover
and interaction rewiring; second, the decomposition responds to
differences in network structure (like connectance) as expected;
finally, the decomposition more accurately captures rewiring than the
proposed alternative using a different denominator put forth by Fründ
(2021).
